---
title: "Prompt Configuration and Wrapper Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Prompt Configuration and Wrapper Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

This vignette explains:

- How to discover providers and models
- Which prompt arguments are available
- How to call models with either the low-level API objects or the one-call wrapper `ask_llm()`
- How to handle common runtime errors

## 1) Choose a Provider and Model

Use provider and model discovery before sending prompts.

```{r}
library(llmModule)

providers <- get_providers(ollama_available = is_ollama_running())
providers

api <- new_BridgedLlmApi(
  provider = "OpenAI",
  api_key = Sys.getenv("OPENAI_API_KEY")
)

models <- get_llm_models(api)
models
```

For local usage with Ollama:

```{r}
manager <- new_OllamaModelManager()
manager <- update(manager)

local_api <- new_LocalLlmApi(manager, "tinyllama")
get_llm_models(local_api)
```

## 2) Prompt Arguments You Can Use

`ask_llm()` forwards extra arguments (`...`) directly to `new_LlmPromptConfig()`.

Core prompt arguments:

- `prompt_content` (required): user prompt text
- `model` (required): model id to call
- `prompt_role`: role for the message (default `"user"`)
- `max_tokens`: max generated tokens (default `100`)
- `temperature`: randomness (default `1.0`)
- `top_p`: nucleus sampling value (default `1`)
- `n`: number of completions (default `1`)
- `stop`: stop sequence(s)
- `seed`: optional numeric seed
- `presence_penalty`: topic novelty bias (default `0`)
- `frequency_penalty`: repetition penalty (default `0`)
- `logprobs`: include token log-probabilities (default `FALSE`)

Note:

- Not every provider/model combination supports every argument.
- If `temperature = 0` and `n > 1`, `n` is forced to `1` to avoid unnecessary token usage.

## 3) One-call Usage with `ask_llm()`

`ask_llm()` is the fastest path for scripts and simple package workflows.

```{r}
result <- ask_llm(
  provider = "OpenAI",
  api_key = Sys.getenv("OPENAI_API_KEY"),
  model = "gpt-4.1",
  prompt_content = "Summarize entropy in one sentence.",
  temperature = 0.2,
  max_tokens = 80,
  top_p = 1,
  n = 1
)

if (!is.null(attr(result, "error"))) {
  message(attr(result, "error"))
} else {
  result$choices[[1]]$message$content
}
```

For local Ollama with the wrapper:

```{r}
local_result <- ask_llm(
  provider = "Ollama",
  model = "tinyllama:latest",
  prompt_content = "Summarize entropy in one sentence.",
  temperature = 0.2
)
```

## 4) Object-based Usage (Low-level Control)

Use this approach when you want explicit API and prompt objects.

```{r}
api <- new_BridgedLlmApi(
  provider = "Anthropic",
  api_key = Sys.getenv("ANTHROPIC_API_KEY")
)

prompt <- new_LlmPromptConfig(
  model = "claude-3-5-sonnet-latest",
  prompt_content = "Write three bullet points on entropy.",
  temperature = 0.3,
  max_tokens = 120
)

result <- send_prompt(api, prompt)
```

## 5) Error Handling Pattern

Network, credential, and provider errors are attached via the `error` attribute.

```{r}
result <- ask_llm(
  provider = "OpenAI",
  api_key = "invalid-key",
  model = "gpt-4.1",
  prompt_content = "Hello"
)

if (!is.null(attr(result, "error"))) {
  message("Request failed: ", attr(result, "error"))
} else {
  cat(result$choices[[1]]$message$content)
}
```

## 6) Recommended Workflow

- Start with `get_providers()` to discover available providers in your environment.
- Create an API object and call `get_llm_models()` to pick a valid model.
- Use `ask_llm()` for concise one-call usage.
- Switch to explicit objects (`new_*` + `send_prompt()`) when you need finer control.
